Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-10 article/article.tex
mozes

\subsection{Training Method and Classifiers}
For each classifier, a "leave one (subject) out" cross validation procedure was used to avoid overfitting. For N=6 iterations, N-1 subjects functioned as training set, while the other subject functioned as validation set. The classifier accuracy is the average accuracy over all interations. 
We compare the following classifiers:

Gaussian Naive Bayes (GNB). This classifier builds a generative model underlying a class, by estimating the means and the standard deviations of the input features from the training set \cite{bk:2004aplay}. It assumes a Gaussian distribution and strongly independent input features. Bayes rule is used to estimate the probability of a class (picture or sentence), given the input features of the validation set. Two approaches were used to estimate the parameters of the model. In the first method, averages of the selected scans belonging to a stimulus were used to estimate the parameters, while in the second method, the parameters were estimated for each scan. In both methods, the resulting probability of a class was the sum of log-likelyhoods per scan and the class with maximum probability was selected. The advantage of the first method is that fewer parameters need to be estimated with greater amount of examples. It thus reduces the space and time complexity, and variance of the model. However, because it is likely that the assumptions of equal means and standard deviations for each scan do not hold, the second approach may decrease the inductive bias and enhance the accuracy.

@@

Multivariate Gaussian.

>>>>

\subsection{Training Method and Classifiers}
For each classifier, a "leave one (subject) out" cross validation procedure was used to avoid overfitting. For N=6 iterations, N-1 subjects functioned as training set, while the other subject functioned as validation set. The classifier accuracy is the average accuracy over all interations. 
We compared the following classifiers:

Gaussian Naive Bayes (GNB). This classifier builds a generative model underlying a class, by estimating the means and the standard deviations of the input features from the training set \cite{bk:2004aplay}. It assumes a Gaussian distribution and strongly independent input features. Bayes rule is used to estimate the probability of a class (picture or sentence), given the input features of the validation set. Two approaches were used to estimate the parameters of the model. In the first method, averages of the selected scans belonging to a stimulus were used to estimate the parameters, while in the second method, the parameters were estimated for each scan. In both methods, the resulting probability of a class was the sum of log-likelihoods per scan and the class with maximum probability was selected. The advantage of the first method is that fewer parameters need to be estimated with greater amount of examples. It thus reduces the space and time complexity, and variance of the model. However, because it is likely that the assumptions of equal means and standard deviations for each scan do not hold, the second approach may decrease the inductive bias and enhance the accuracy.

@@

Multivariate Gaussian (MVG). In MVG, independence between feature vectors is not assumed. Instead, the mutivariate distrbution is used to estimate the probability of the classes, with the covariance matrix and the means as parameters. Again, the increase in parameters to be estimated compared to GNB (the correlations) may decrease generality, while also decreasing inductive bias.
